Universal Anonymous Signatures

### 2022-10-04 prism-backend/research/gsac/introduction-paper.tex
Spellchecked abstract and intro.

GS schemes enhance utility after authentication, allowing partial
re-identification like linking of signatures, or even full deanonymization.
While actual applications of group signatures seem hard to find in the real
world, Direct Anonymous Attestation (DAA) \cite{bcc04,bl07,cdl16b} has been
deployed to millions of computing devices into what's called TPM (Trusted
Privacy Module)%
\footnote{\url{https://trustedcomputinggroup.org/resource/trusted-platform-module-tpm-summary/}. Last access, June 18th, 2022.}.
Indeed, DAA is a very close relative of group signatures, where the signer is
divided into two components (trusted and partially trusted), and signing
and verification are interactive.

%% Previous works summary w/ refs directly related contribs of UAS
%% (or, tech approaches of main precedents)
\paragraph{Evolution of AC and GS.} %
AC and GS systems have followed separate paths, with exceptions.
Functionality-wise, Attribute-Based Group Signatures add attributes to the
credentials issued to group members, who can later use them to prove fixed
claims \cite{emo09,aa14}. Hidden identity-based signatures also add attributes
to the credentials, to prevent the opener (the trusted party who
can deanonymize signers) from having to rely on the issuer in order to return
meaningful identifying information when opening a signature \cite{ks07}. Some AC
schemes also incorporate some utility after authentication, like
revocable AC schemes \cite{cks10}.

@@

AC and GS have experienced remarkable efforts towards generalisation. In
the AC domain, malleable signatures are used as core building block in
\cite{cklm14}, to allow building both conventional AC and Delegatable AC
systems, depending on the transformation supported by the malleable signatures.
Also, \cite{ckl+15} gives a very generic approach to build AC schemes. In GS,
very recently, BiAS \cite{lnpy21} and MPS \cite{ngsy22} flexibilize the
trade-off between anonymity and accountability.

%% Main drawbacks of precedents
\paragraph{Limitations of GS and AC.} %
Even the independent generalisation efforts in both GS and AC
have limited applicability in the real world. On the GS side, although MPS
achieves a powerful balance on when a signature is deanonymizable and what
information can be extracted, upon closer look, this information is somehow
meaningless. Namely, the notion of identity is not well defined and, thus, it is
not possible to assess whether the value output by their generalised open
function makes sense or even if it is legitimate. Also, proving membership at
signing time is typically not enough. In other words, in GS,
utility at authentication time is very limited. This is precisely the main
strength in AC schemes, which also have a well defined notion of identity via
attributes. Conversely, the notion of accountability  is barely present in AC
schemes. For instance, non-frameability is not even considered, and it is
non-frameability what prevents honest users from being held accountable of
dishonest actions they did not take part in.
%
In any case, perhaps the most impractical limitation of all is that too many
models exist in both fields. Although similar, each model focuses on slightly
different utility variants, making them hardly comparable. To the best of our
knowledge, no model exists that combines both fields, in a general enough
manner. In practice, needing to resort to too specific models forces system
designers to decide which feature they do not want to lose -- or, which one they
will lose.

@@

We observe that in all GS and AC models, concrete
claims related to user knowledge are proven either at issuance, signature
generation, and opening times. Typically, at issuance time, the user proves
knowledge of a secret key; at signing time, she proves that her secret key (and,
potentially, more attributes) has been attested by some issuer; finally, at
opening time, the opener proves that some fixed user-related information is
contained in the de-anonymized signature.

@@

But the flexibility obtained from combining models from the AC and GS
domains into one also brings complexity. For instance, in order to meet
the general practice in AC, our UAS model includes multiple issuers. Along with
the combination of GS features, this paves the way to including multiple
openers, each with its own opening functionality. While powerful from a
practical point of view, this introduces similar (unavoidable?) limitations
privacy-wise as in functional encryption schemes \cite{bsw11} -- e.g., revealing
too granular information at signing or opening time reduces privacy. However, on
this occasion, signers control ``how deanonymizable'' their signatures will
be, and know it at signature generation time. This flexibility on the opening
values also leads to the need of using extraction-based techniques for the
modelling, since we cannot expect that opening outputs the real identity of the
signer. This is no surprise, though, as it was already observed in GS schemes
with non-conventional opening \cite{dl21}, in DAA schemes \cite{cdl16,cdl16b}.
In fact, simulation-extractability seems to be most useful here, something that
was also observed in \cite{cl06} for producing signatures out of knowledge of
witnesses for concrete NP statements.

\paragraph{Generic construction.} %
We give \CUASGen, a generic construction of UAS based on well-known
building blocks, and prove its security. Despite its functional flexibility, our
construction is simple. Like many previous related schemes, credentials are
signatures over blocks of messages -- each message encoding a different
attribute. Users simultaneously leveraging multiple credentials need to prove
that they are bound to the same key. Utility information to be revealed at
signing time is output in plaintext, and utility information extractable by
openers is encrypted under their public key -- in both cases, users prove
correct computation.

The three functional placeholders mentioned above are \fissue, \feval, and
\finsp. \fissue is the function that users are required to evaluate at issuance
time, to prove knowledge of a user key and, potentially, claims over attributes
in previously obtained credentials. \feval is computed at signing time by the
user, and controls and proves correctness of the information learned by
verifiers. Finally, \finsp, although  computed also at signing time by the
users, proves correctness of the utility information extractable after signing.
The latter is, in addition, fed and modulated with the output of \feval. With
these functions, we allow achieving configurable utility-vs-privacy tradeoffs
throughout the whole ``lifecycle'' (from issuance to opening). They also take
a central role in defining the NP statements that need to be proven by different
algorithms/protocols, summarised in \figref{fig:proof-blocks-uas}.

@@

\paragraph{Universality.}
To formally showcase that UAS can indeed claim to be universal, we prove that
restrictions of our generic construction imply the GS and AC ancestors of UAS.
This includes not only their vanilla versions, but also relevant variants,
such as MPS \cite{ngsy22}, (a modified version of) group signatures with
message-dependent opening \cite{seh+12}, or anonymous credentials with
revocation \cite{cks10} or delegation \cite{bcc+09}.
%
Strictly speaking, for AC schemes, we build on a simple transform of our main
construction and model that turns non-interactive signatures into interactive
authentication protocols with protection against replays\footnote{This is
  the well-known folklore approach that has the verifier send a fresh nonce to
  be signed by the alleged owner of the private key related to a known
  public key.}. We further build ring signatures (RS) in the model given by
\cite{bkm06}, from an alternative UAS construction that improves issuer privacy.
%
The most interesting part being that, while we prove implications with
previously known schemes, our approach allows to merge their features: e.g.,
one can easily instantiate GSs with with no revocation at all, ACs
with full de-anonymization, RS with linkability, etc.

@@

\paragraph{Sample real-world use cases.} %
By enabling customization at issuance, signing and opening times, as well as
multiple uncoupled issuers and openers, the possibilities are large and
especially useful in contexts where different parties may have different
privacy-vs-utility tradeoffs. As an example, consider a social network that
requires under-age users to get permission from one parent. This can be defined
via a delegatable credential scheme, checking that the delegation chain of the
user requesting to join is valid via a policy at issuance time. Later, in order
to make some post in the system advertising something to be sold in a local
second-hand page in the social network, the user may need to reveal, at signing
time, being a citizen of the local area (e.g. city). This can be done via an
appropriate policy at signing time. If, after the product is sold, it proves
to be defective, the social network may directly output the email of the user
if s/he is over-age, or the email of the adult in charge if s/he is under-age.
And that could be achieved via a policy for utility at opening time. Finally,
if, in the same social network, some other
issuer-user-verifier situation comes up that requires a different set of utility
choices, just the appropriate functions would need to be changed, without the
need to re-model from scratch (or at all).

>>>>

GS schemes enhance utility after authentication, allowing partial
re-identification like linking of signatures, or even full deanonymisation.
While actual applications of group signatures seem hard to find in the real
world, Direct Anonymous Attestation (DAA) \cite{bcc04,bl07,cdl16b} has been
deployed to millions of computing devices into what's called TPM (Trusted
Privacy Module)%
\footnote{\url{https://trustedcomputinggroup.org/resource/trusted-platform-module-tpm-summary/}. Last access, June 18th, 2022.}.
Indeed, DAA is a very close relative of group signatures, where the signer is
divided into two components (trusted and partially trusted), and signing
and verification are interactive.

%% Previous works summary w/ refs directly related contribs of UAS
%% (or, tech approaches of main precedents)
\paragraph{Evolution of AC and GS.} %
AC and GS systems have followed separate paths, with exceptions.
Functionality-wise, Attribute-Based Group Signatures add attributes to the
credentials issued to group members, who can later use them to prove fixed
claims \cite{emo09,aa14}. Hidden identity-based signatures also add attributes
to the credentials, to prevent the opener (the trusted party who
can deanonymise signers) from having to rely on the issuer in order to return
meaningful identifying information when opening a signature \cite{ks07}. Some AC
schemes also incorporate some utility after authentication, like
revocable AC schemes \cite{cks10}.

@@

AC and GS have experienced remarkable efforts towards generalisation. In
the AC domain, malleable signatures are used as core building block in
\cite{cklm14}, to allow building both conventional AC and Delegatable AC
systems, depending on the transformation supported by the malleable signatures.
Also, \cite{ckl+15} gives a very generic approach to build AC schemes. In GS,
very recently, BiAS \cite{lnpy21} and MPS \cite{ngsy22} flexibilise the
trade-off between anonymity and accountability.

%% Main drawbacks of precedents
\paragraph{Limitations of GS and AC.} %
Even the independent generalisation efforts in both GS and AC
have limited applicability in the real world. On the GS side, although MPS
achieves a powerful balance on when a signature is deanonymisable and what
information can be extracted, upon closer look, this information is somehow
meaningless. Namely, the notion of identity is not well defined and, thus, it is
not possible to assess whether the value output by their generalised open
function makes sense or even if it is legitimate. Also, proving membership at
signing time is typically not enough. In other words, in GS,
utility at authentication time is very limited. This is precisely the main
strength in AC schemes, which also have a well defined notion of identity via
attributes. Conversely, the notion of accountability  is barely present in AC
schemes. For instance, non-frameability is not even considered, and it is
non-frameability what prevents honest users from being held accountable of
dishonest actions they did not take part in.
%
In any case, perhaps the most impractical limitation of all is that too many
models exist in both fields. Although similar, each model focuses on slightly
different utility variants, making them hardly comparable. To the best of our
knowledge, no model exists that combines both fields, in a general enough
manner. In practice, needing to resort to too specific models forces system
designers to decide which feature they do not want to lose -- or, which one they
will lose.

@@

We observe that in all GS and AC models, concrete
claims related to user knowledge are proven either at issuance, signature
generation, and opening times. Typically, at issuance time, the user proves
knowledge of a secret key; at signing time, she proves that her secret key (and,
potentially, more attributes) has been attested by some issuer; finally, at
opening time, the opener proves that some fixed user-related information is
contained in the deanonymised signature.

@@

But the flexibility obtained from combining models from the AC and GS
domains into one also brings complexity. For instance, in order to meet
the general practice in AC, our UAS model includes multiple issuers. Along with
the combination of GS features, this paves the way to including multiple
openers, each with its own opening functionality. While powerful from a
practical point of view, this introduces similar (unavoidable?) limitations
privacy-wise as in functional encryption schemes \cite{bsw11} -- e.g., revealing
too granular information at signing or opening time reduces privacy. However, on
this occasion, signers control ``how deanonymisable'' their signatures will
be, and know it at signature generation time. This flexibility on the opening
values also leads to the need of using extraction-based techniques for the
modelling, since we cannot expect that opening outputs the real identity of the
signer. This is no surprise, though, as it was already observed in GS schemes
with non-conventional opening \cite{dl21}, in DAA schemes \cite{cdl16,cdl16b}.
In fact, simulation-extractability seems to be most useful here, something that
was also observed in \cite{cl06} for producing signatures out of knowledge of
witnesses for concrete NP statements.

\paragraph{Generic construction.} %
We give \CUASGen, a generic construction of UAS based on well-known
building blocks, and prove its security. Despite its functional flexibility, our
construction is simple. Like many previous related schemes, credentials are
signatures over blocks of messages -- each message encoding a different
attribute. Users simultaneously leveraging multiple credentials need to prove
that they are bound to the same key. Utility information to be revealed at
signing time is output in plain text, and utility information extractable by
openers is encrypted under their public key -- in both cases, users prove
correct computation.

The three functional placeholders mentioned above are \fissue, \feval, and
\finsp. \fissue is the function that users are required to evaluate at issuance
time, to prove knowledge of a user key and, potentially, claims over attributes
in previously obtained credentials. \feval is computed at signing time by the
user, and controls and proves correctness of the information learned by
verifiers. Finally, \finsp, although  computed also at signing time by the
users, proves correctness of the utility information extractable after signing.
The latter is, in addition, fed and modulated with the output of \feval. With
these functions, we allow achieving configurable utility-vs-privacy trade-offs
throughout the whole ``life-cycle'' (from issuance to opening). They also take
a central role in defining the NP statements that need to be proven by different
algorithms/protocols, summarised in \figref{fig:proof-blocks-uas}.

@@

\paragraph{Universality.}
To formally showcase that UAS can indeed claim to be universal, we prove that
restrictions of our generic construction imply the GS and AC ancestors of UAS.
This includes not only their vanilla versions, but also relevant variants,
such as MPS \cite{ngsy22}, (a modified version of) group signatures with
message-dependent opening \cite{seh+12}, or anonymous credentials with
revocation \cite{cks10} or delegation \cite{bcc+09}.
%
Strictly speaking, for AC schemes, we build on a simple transform of our main
construction and model that turns non-interactive signatures into interactive
authentication protocols with protection against replays\footnote{This is
  the well-known folklore approach that has the verifier send a fresh nonce to
  be signed by the alleged owner of the private key related to a known
  public key.}. We further build ring signatures (RS) in the model given by
\cite{bkm06}, from an alternative UAS construction that improves issuer privacy.
%
The most interesting part being that, while we prove implications with
previously known schemes, our approach allows to merge their features: e.g.,
one can easily instantiate GSs with with no revocation at all, ACs
with full deanonymisation, RS with linkability, etc.

@@

\paragraph{Sample real-world use cases.} %
By enabling customisation at issuance, signing and opening times, as well as
multiple uncoupled issuers and openers, the possibilities are large and
especially useful in contexts where different parties may have different
privacy-vs-utility trade-offs. As an example, consider a social network that
requires under-age users to get permission from one parent. This can be defined
via a delegatable credential scheme, checking that the delegation chain of the
user requesting to join is valid via a policy at issuance time. Later, in order
to make some post in the system advertising something to be sold in a local
second-hand page in the social network, the user may need to reveal, at signing
time, being a citizen of the local area (e.g. city). This can be done via an
appropriate policy at signing time. If, after the product is sold, it proves
to be defective, the social network may directly output the email of the user
if s/he is over-age, or the email of the adult in charge if s/he is under-age.
And that could be achieved via a policy for utility at opening time. Finally,
if, in the same social network, some other
issuer-user-verifier situation comes up that requires a different set of utility
choices, just the appropriate functions would need to be changed, without the
need to re-model from scratch (or at all).

### 2022-10-04 prism-backend/research/gsac/uas-paper.tex
30 pages.
Spellchecked abstract and intro.

%% Set/unset to activate/deactivate author comments
\def\authnotes{0}

@@

\title{Universal Anonymous Signatures}
\author{Jesus Diaz\inst{1} \and Markulf Kohlweiss\inst{2}}

\institute{Input Output Global,\\
\email{jesus.diazvico@iohk.io},\\
\and
Input Output Global and University of Edinburgh,\\
\email{markulf.kohlweiss@ed.ac.uk}}

@@

  Our main theoretical contribution is thus unifying previously separate (albeit
  close) systems under the same generalised model. Such unified model also
  allows to, very easily, build ``hybrid'' systems combining features of its
  ancestors: e.g., anonymous credentials with conditional deanonymization based
  on their attributes.

  In practice, this means that cryptographic engineers and system designers
  can reach the desired utility-vs-privacy tradeoff that best suits their needs,
  just by defining a few functions -- but without needing to model and prove
  security from scratch or implement a whole system.
\end{abstract}

>>>>

%% Set/unset to activate/deactivate author comments, anonymous submission, etc.
\def\authnotes{0}
\def\anonymous{1}

@@

\title{Universal Anonymous Signatures}
\ifnum\anonymous=1
\author{}
\institute{}
\fi
\ifnum\anonymous=0
\author{Jesus Diaz\inst{1} \and Markulf Kohlweiss\inst{2}}
\institute{Input Output Global,\\
\email{jesus.diazvico@iohk.io},\\
\and
Input Output Global and University of Edinburgh,\\
\email{markulf.kohlweiss@ed.ac.uk}}
\fi

@@

  Our main theoretical contribution is thus unifying previously separate (albeit
  close) systems under the same generalised model. Such unified model also
  allows to, very easily, build ``hybrid'' systems combining features of its
  ancestors: e.g., anonymous credentials with conditional deanonymisation based
  on their attributes.

  In practice, this means that cryptographic engineers and system designers
  can reach the desired utility-vs-privacy trade-off that best suits their needs,
  just by defining a few functions -- but without needing to model and prove
  security from scratch or implement a whole system.
\end{abstract}
